### 2019-03-18 README.Rmd
Add citation information

```{r authors, echo = FALSE, results = 'asis'}
unclass(desc::desc_get_authors(here::here("DESCRIPTION"))) %>%
  purrr::keep(~"aut" %in% .$role) %>%
  purrr::map_chr(~paste(.$given, .$family)) %>%
  glue::glue_collapse(sep = ", ", last = ", and ") %>%
  paste0("Authors: _", ., "_") %>%
  cat()
```

@@

>>>>

```{r authors, echo = FALSE, results = 'asis'}
unclass(desc::desc_get_authors(here::here("DESCRIPTION"))) %>%
  purrr::keep(~"aut" %in% .$role) %>%
  purrr::map_chr(~paste(.$given, .$family)) %>%
  glue::glue_collapse(sep = ", ", last = " and ") %>%
  paste0("Authors: _", ., "_") %>%
  cat()
```

@@

### Citation

If you use **citesdb** in a publication, please cite both the package and source data:

```{r, results = "asis"}
print(citation("citesdb"), style = "textVersion")
```
